---
title: "p8105_hw5_yl4613"
author: "YuechenLiu"
date: "11/17/2020"
output: github_document
---
############ HW5 ################
```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(purrr)
knitr::opts_chunk$set(echo = TRUE)
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read.csv('data/homicide-data.csv') %>% 
  mutate(
    city_state = str_c(city, state, sep = "-"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa-AL")
```

Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == 'unsolved')
  )

```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% 
    filter(city_state == "Baltimore-MD") %>% pull(hom_unsolved),
  aggregate_df %>% 
    filter(city_state == "Baltimore-MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate .....

```{r}
results_df =
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)

```


```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin =  conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

## Problem 2

Import and tidy the dataset
```{r}
path_df = 
  tibble(
  path = list.files('data_2')) %>% 
  mutate(path = str_c('data_2/',path),
         data = purrr::map(.x = path, ~read.csv(.x))) %>% 
  unnest(data) %>% 
  separate(
    path, into = c('data', 'info'),sep = '/'
  ) %>% 
  separate(
    info, into = c('information', 'csv'), sep = '.csv'
  ) %>% 
  select(-data, -csv) %>% 
  separate(
    information, into = c('arm', 'id'), sep = '_'
  ) %>% 
  mutate(
    arm = case_when(
      arm == "con" ~ "control",
      arm == "exp" ~ "experimental")) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = 'week',
    names_prefix = 'week_',
    values_to = 'observation')
###End of tidying
```

Spaghetti plot---
```{r}
path_df %>% 
  ggplot(
  aes(x = week, y = observation, group = interaction(id, arm)))+
  geom_line(aes(color = arm))+ 
  labs(title = 'Observations on each subject over time')

```


Comment: Two arms of subjects have very similar initial observations. However, after 8 weeks, the experimental group has generally higher observations, while control group observations has almost no change in range of value between its subjects.



## Problem 3
```{r}
n = 30
sigma = 5
```

Set up function--given n, mu, sigma. return mean and p-value.
```{r}
sim_1 = function(n, mu, sigma) {  
  x = rnorm(n, mean = mu, sd = sigma)
  t_test = broom::tidy(t.test(x))
  result =
    tibble(
    mu_hat = mean(x),
    pvalue = t_test$p.value
    )
  return(result)
}
```


Function: generate 5000 datasets. Use a for loop.
```{r}
sim_5000 = function(mean) {
  output_5000 = vector("list", length = 5000)
  for (i in 1:5000) {
    output_5000[[i]] = sim_1(n, mean, sigma)}
  result_5000 = bind_rows(output_5000)
  return(result_5000)
  }

```

Simulation---mu = 0 (5000 times)
```{r}
set.seed(1911)
sim_0 = sim_5000(0)
```

Function--showing the proportion of times the null was rejected
```{r}
proportion = function(sim) {
  reject = 
    sum(sim$pvalue < 0.05) / 5000
  return(reject)
}
```

Repeat the above for mu = {1,2,3,4,5,6} (Total result: a list including when mu from 0 to 6)
```{r}
set.seed(1911)
sim_16 = vector("list", length = 7)
for (i in 0:6) {
  sim_16[[i+1]] = proportion(sim_5000(i))
}
```


Plot time!
```{r}


```


```{r}


```


```{r}


```



```{r}


```


```{r}


```